Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-27 article.qmd
Simulation as figure

To simulate a system,
we create a `Simulator` instance,
which compiles a given system and interfaces with solvers.
By default, it creates a first-order ordinary differential equation (ODE) system
using `numpy` as a backend.
The Simulator wraps the output in a `pandas.DataFrame`,
which can be easily plotted with the standard `plot` method.

```{python}
import numpy as np
from poincare import Simulator

sim = Simulator(Oscillator)
df = sim.solve(save_at=np.linspace(0, 5, 101))

df
```

```{python}
df.plot();
```

>>>>

To simulate a system,
we create a `Simulator` instance (@fig-sim),
which compiles a given system and interfaces with solvers.
By default, it creates a first-order ordinary differential equation (ODE) system
using `numpy` as a backend.
The Simulator wraps the output in a `pandas.DataFrame`,
which can be easily plotted with the standard `plot` method.

::: {#fig-sim layout=[[1],[1,1]]}
```{python}
import numpy as np
from poincare import Simulator

sim = Simulator(Oscillator)
df = sim.solve(save_at=np.linspace(0, 5, 101))
```

```{python}
df.head()
```

```{python}
df.plot(figsize=(4, 2))
```

Simulation of the `Oscillator` system from @fig-second-order,
which outputs a `pandas.DataFrame`.
:::
